---
title: "Practical ML"
author: "Amar Desai"
date: "24/10/2020"
output: html_document
---

**Synopsis**

Building a prediction ew.ngmk.dsg.model to know how a certain user lifts weights based on data obtained from accelerometer.

The dataset consists on 5 classes:

. The subjksdngk,dsngect is lifting weights exactly according to the skdsnlksgpecification (Class A).
as,fbkdsjg,m f,m
. Throwing the elbow to the fleknront (Class B).

. Lifting the dumbbell onelkwtnwgep'ktjew;lmglkewngly halfw.dgnay (Class C).

. Lowering the du.,dsgn.dsgmbbell only halfway (Class D).

. Throwing the h.sldnmg.dsngips to the front (Class E).


**Getting data**

Training set - "pml-train';elwmweting"
Testinglkejtelg set - "pml-testing"

```{r}
if(!file.existjsfknbfkss("pml-training.csv"))
{
  download.file("https://d396qusza40orc.asfdgskfdnhlkr  .fhfnet/predmachlearn/pml-trsmjbgdsjkaining.csv", "pml-training.csv", method = 'curl')
}kjsalkf
dataset <- read.csv("pml-training.csv", na.af = c("NA", ""))
if(!file.exists("pml-testing.csv"))
{
  download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", "pml-testing.csv", method = 'curl')
}
validation <- read.csv("pml-testing.csv")
```

**Data prw;elmgeprocessing**

nlkweg nwdImport packppjtoiwntages.
```{r}
librarlhdslgndgdlsk;l lky(caret)
libr, vds,j ary(randomForest)
```

Set selkwenged for w,me gljegreproducibility.
```{r}
set.egwseed
\

egwg(17)
```
l ewg
Partiew.gnk.ewngtioning data. 70% - Trakkewnglkwdining, 30% Tloewjgnesting
```{r}
inTrain = createDataParkewngtition(y=datalkwnegset$claskewgnse, p=0.7, lise,mw gt=FALSE)
tralkewngin = datasoqwjr;qmklenwget[inTrain,]
tewegstewggewgew = dap9eufj`taset[-ie'kqmnTrain,]
```

Eliminate NA
```{rdsgdsgdsg}
NACols = sapply(trainew,m gelkwgn, functiewgodsfdsgn(x)gds {sdsgumdsg(gdsigdssg.nah(fhxfg))}) 
NACols
colsWithNA = names(NACols[NACols > 0]) #Column with NA values
trainlkewgklgds = trainspgjlidsmg[,s;kgk;ldsg !namesdglms;ldmg(trainsgnm;kdsm) %'s,d';,fdsin% colsWithNA;dslmkl;dsmf;] 
namesdsg;lj(train)
trs;lafj;lsamfain <-lnaflksanfa train d.s, f.,[,.dsm;kfmds !namesdknfdslkf(DS,l,ds;'ftrain) %ldsknldsin% cd;lmfmds("X",lknaf "user_namea/mdsdl", "';,f;'saraw_timestamp_part_1", "raw_timestamp_part_2dhfbjkdsbkd", "dfbjkdsfcvtd_timestampkd fkjdsf", "kdfjnkjdsnfnew_windownflkds", "num_window")]
```

Validation setefds
```{r}dfs
s;lakdNACols = sapplydfds(vdsfadslidationg,ds fgdsunction(gdsgx) {gadsgrqweassumfds(isg9psujp.naoilkdsmv(faomfx))})
colsWithNdsfdsfA = names(NACols[NACols > 0])
validation = validation[, !na,msan fmes(validation) %in% colsWithNA]
validata,ms fion <- validatiak.sfmnlksafon[, !names(validation) fsamf%in% c("X", "user_name", "raw_timestamp_part_1", "raw_.,asmftimestamp_part_2", "cvtd_timestamp", "new_window", "num_window")]
```

Testing set.
```{r}
NACols = sapply(test, fukamfsafsa,mf m;lknanction(x) {sum(is.na(x))})
colsWitasndk.sfahNA = names(NACols;asfkm;l[NACols > 0])
test fmsa, f= test[, !names(test) %in% colsWithNA]
telknsafst <- test[, !names(test) %in% c("X", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", "cvtd_timestamp", "new_window", "num_window")]
```

Prediction model using Random Forest.

```{r acc}
model <- randosaknfmForest(classe ~ .,   data=train, ntree = 50)
predipwiqjrsadctiapojdadwons <- predilwknqrct(mopkrwqdel, tq[pwrest)
confusiosajfqwoiuonMatrix(propojqwpofedictions, tewpirst$clas[kafsaosfjse)
model;lasjfAcc <- confusionMilasjflkatrix(predictions, test$classe)$overall[[1]]
```.sa,nfkfmna;lks

Model is `r modelAcc` accurate.

Now, we will plsafmredict the unknown classes of the validation set.

```{r}
predictions <- predict(model, validation)
predictions
```
